\bf Tearing Mode Dynamics in Tokamak Plasmas

### 2021-12-03 Documentation/TearingModeTheory.tex
Corrections

\subsection{Resonant Layer Physics}\label{sres}
By analogy with Equation~(\ref{e133}), we can write
\begin{equation}\label{e134}
{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\omega\,{\mit\Psi}_s\right).
\end{equation}
Here, $\tau_s$ is the {\em reconnection time}\/ (i.e., the typical timescale on which magnetic reconnection takes place in the
resonant layer surrounding the resonant surface), whereas $\omega$ is the phase velocity 
of the tearing mode when the wall is perfectly conducting. The
phase velocity  is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
flow (Fitzpatrick 1993). (See Sections~\ref{s6.2} and \ref{sphase1}.)

@@

\subsection{No-Slip Constraint}\label{sns}
The reconnected magnetic flux at the resonant surface is assumed to convected by the local plasma flow. (See Section~\ref{sres}.) Hence, changes in the
plasma flow at the resonant surface induced by the electromagnetic torques that develop in the vicinity of this
surface will modify the convection velocity. Consequently, the phase velocity of the tearing mode can be written
\begin{equation}\label{e200}
 \omega(t) = \omega_{0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
 \omega_{0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
\end{equation}
where $\omega_{0}$ is the unperturbed phase velocity. The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980). 
It follows from Equations~(\ref{e190})
and (\ref{e191}) that
\begin{equation}\label{e201}
\omega(t) = \omega_{0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
\end{equation}
(See Section~\ref{stb}.)

\subsection{Final Equations}
Equations~(\ref{e123}), (\ref{e133}), (\ref{e134}),  (\ref{e145})--(\ref{e151}), (\ref{e198}), (\ref{e199}), and (\ref{e201})
can be combined to give the following complete set of equations that determine the time evolution of the reconnected 
magnetic flux at the resonant surface:
\begin{align}\label{e202}
{\mit\Delta\hat{\Psi}}_s\equiv \tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\omega\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
\tau_w\,\frac{d\hat{\mit\Psi}_w}{dt} &= E_{sw}\,\hat{\mit\Psi}_s +\tilde{E}_{ww}\,\hat{\mit\Psi}_w
+\hat{I}_c,\label{e203}\\[0.5ex]
\omega(t)& = \omega_{0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\label{e210a}\\[0.5ex]
(1+2\,q_s^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1\,p}^{\,2}}{\tau_{M}}\right)\alpha_p
&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1\,p})]^{\,2}}
\,{\rm Im}({\mit\Delta\hat{\Psi}}_s\,\hat{\mit\Psi}_s^{\,\ast}),\label{e205}\\[0.5ex]
\frac{d\beta_p}{dt} + \frac{j_{0\,p}^{\,2}}{\tau_{M}}\,\beta_p
&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0\,p})]^{\,2}}\,
{\rm Im}({\mit\Delta\hat{\Psi}}_s\,\hat{\mit\Psi}_s^{\,\ast}).\label{e206}
\end{align}
Here, 
\begin{align}
\hat{I}_c &= \left(\frac{r_w}{r_c}\right)^m\frac{\mu_0\,I_c}{R_0\,B_z},\\[0.5ex]
\tilde{E}_{ww} &= E_{ww} + \frac{2m\,(r_w/r_c)^{2m}}{1-(r_w/r_c)^{2m}}.\label{e208}
\end{align}

\section{Reduced Resonant  Response Model}\label{ff}
\subsection{Introduction}
Equations~(\ref{e202})--(\ref{e206}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
phase velocity, $\omega_{0}$---that can only be determined by solving for the plasma response in the radially-thin resonant layer surrounding the resonant surface. Unfortunately, determining the resonant plasma response is not a straightforward task. The
problem is that the small characteristic lengthscale in the resonant region (i.e., the resonant layer width) causes the fundamental ordering parameters
$\delta_e$ and $\delta_i$ (see Section~\ref{s3.9}) to take values that are of order unity. Consequently, most of the simplifications described in
Section~\ref{lowest} are not applicable in the resonant layer. In particular, many of the terms in the Braginskii equations (see Section~\ref{sbrag}) that are negligible in the outer region (e.g., plasma resistivity) have to be taken into account in the resonant layer.

@@

\subsection{Derivation of Linear Layer Equations}\label{s5.3}
Suppose that the system is perturbed by a tearing mode with $m$ periods in the poloidal direction, and
$n$ periods in the toroidal direction. In accordance with Equations~(\ref{e287})--(\ref{e290}), and (\ref{e292})--(\ref{e293}), we can write
\begin{align}\label{e295}
\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
U(\hat{x},\zeta,\hat{t}) &=  \hat{\nabla}^2\tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e300}
\end{align}
where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the phase velocity of the tearing mode in the laboratory frame. 
Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear layer equations:
\begin{align}\label{e301}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} \\[0.5ex]
&\phantom{=}
+S^{-1}\,P_\parallel\!\left(m\,\omega_{\ast\,e}\,\tau_H\,\hat{x}\,\tilde{\psi}-\frac{m}{\hat{L}_s}\,\hat{x}^2\,\tilde{N}\right)
+ S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\nonumber\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e304}
\end{align}
Here, 
\begin{equation}\label{e313a}
\tau_H = \frac{L_s}{m\,V_A}
\end{equation}
is the {\em hydromagnetic time}, 
\begin{equation}
\omega_E = \left(\frac{m}{r_s}\right)V_E(r_s)
\end{equation}
  the 
{\em E-cross-B frequency}, 
\begin{equation}
\omega_{\ast\,e} = -\left(\frac{\tau}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
\end{equation}
  the {\em electron diamagnetic
frequency},
\begin{align}\label{omegai}
  \omega_{\ast\,i} &= \left(\frac{1}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
  \end{align}
    the {\em ion diamagnetic
frequency}, 
\begin{equation}
S=\frac{\tau_R}{\tau_H}
\end{equation}
 the {\em Lundquist number}, 
\begin{equation}\label{e317a}
\tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel}
\end{equation}
 the
{\em resistive diffusion time}, 
\begin{equation}\label{e318a}
\tau_\varphi
= \frac{r_s^{\,2}}{\chi_\varphi}=\frac{r_s^{\,2}\,n_0\,m_i}{\mu_\perp(r_s)}
\end{equation} 
the {\em toroidal momentum confinement time}, and 
\begin{equation}
\tau_\perp = \frac{r_s^{\,2}}{D_\perp}
\end{equation}
 the {\em particle/energy confinement time}. Furthermore, $P_\varphi = \tau_R/\tau_\varphi$, $P_\perp = \tau_R/\tau_\perp$, 
$P_\parallel=\tau_R/\tau_\parallel$, and $\tau_\parallel =r_s^{\,2}/D_\parallel$.

@@

Suppose that the resonant layer lies in a constant-$\psi$ response regime. According to Equation~(\ref{e295}),
the perturbed magnetic flux in the layer takes the form:
\begin{equation}
\hat{\psi}(\hat{x},\zeta,\hat{t}) = \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},
\end{equation}
where $\tilde{\psi}$ is a complex constant. Of course, the physical flux is the real part of the previous expression; that is,
\begin{equation}\label{e352a}
\hat{\psi}(\hat{x},\xi)= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ |\tilde{\psi}|\,\cos\xi,
\end{equation}
where
\begin{equation}
\xi = \zeta +{\rm arg}(\tilde{\psi})-\hat{\omega}\,\hat{t} = m\,\theta-n\,\varphi +{\rm arg}(\tilde{\psi}) -\omega\,t.
\end{equation}
Now, it is clear from Equation~(\ref{e279}) that ${\bf B}\cdot\hat{\nabla}\hat{\psi}=0$. In other words, the contours of
$\hat{\psi}(\hat{x},\xi)$ map out the perturbed magnetic flux-surfaces in the vicinity of the resonant layer. 
Let $\hat{W} = 4\,(\hat{L}_s\,|\tilde{\psi}|)^{1/2}$. Equation~(\ref{e352a}) can be written
\begin{equation}
\frac{\hat{\psi}(\hat{x},\xi)}{|\tilde{\psi}|} = 8\left(\frac{\hat{x}}{\hat{W}}\right)^2 + \cos\xi.
\end{equation}
Figure~\ref{f2a} shows the contours of $\hat{\psi}(\hat{x},\xi)$ specified by the previous equation. It can be seen that the
tearing mode has reconnected magnetic field-lines to produce a {\em helical magnetic island chain}\/ centered on the resonant
surface ($\hat{x}=0$). The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the phase velocity $\omega$. The maximum full (as opposed to half) radial width of the magnetic separatrix is 
\begin{equation}\label{e355s}
W =  \hat{W}\,r_s= 4\,(\hat{L}_s\,|\tilde{\psi}|)^{1/2}\,r_s = 4\left(L_s\,R_0\,|\hat{\mit\Psi}_s|\right)^{1/2},
\end{equation}
where ${\mit\Psi}_s = r_s\,B_z\,\tilde{\psi}$ is the reconnected magnetic flux defined in Equation~(\ref{e99}), and
$\hat{\mit\Psi}_s= {\mit\Psi}_s/(R_0\,B_z)$.

@@

\subsection{Linear Dispersion Relation}\label{s6.2}
Let us write
\begin{equation}\label{e350}
\omega = {\rm i}\,\gamma+\omega_r,
\end{equation}
where $\gamma$ is the growth-rate of the tearing mode, whereas $\omega_r$ is the real
phase velocity of the mode in the laboratory frame. We shall assume that $|\gamma|\ll |\omega_r|$. This assumption can
easily be verified {\em a posteriori}. Asymptotic matching between the solution in the outer region and that in the
thin linear layer surrounding the resonant surface yields a linear tearing mode dispersion relation of the form
\begin{equation}\label{e352}
S^{1/3}\,\hat{\mit\Delta}(\gamma,\omega_r) = E_{ss},
\end{equation}
where use has been made of Equations~(\ref{e110}) and (\ref{e312}). Here, $E_{ss}$ is the real tearing stability index, 
whereas the complex layer matching parameter, $\hat{\mit\Delta}$, is defined in Equation~(\ref{e311}).

@@

Suppose that $Q_\ast\gg P\,p^2$ and $P\ll Q_\ast\,D^2$. It follows that $\nu=1/2$ and
\begin{equation}
C = {\rm i}\left(\frac{\tau}{1+\tau}\right)\frac{Q_\ast}{D^2}.
\end{equation} 
Hence, 
\begin{equation}
\hat{\mit\Delta} = {\rm e}^{{\rm i}\,\pi/4}\,\pi\,\hat{\gamma}\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{Q_\ast^{1/2}}{D},
\end{equation}
and $p_\ast\sim D/Q_\ast^{1/2}$. This so-called {\em semi-collisional regime}\/ is valid when $P\ll Q_\ast^{\,2}/D^2$ and
$P\ll Q_\ast\,D^2$. 
The corresponding tearing mode growth-rate is
\begin{equation}\label{e368}
\gamma = \frac{E_{ss}}{\sqrt{2}\,\pi}\,\frac{d_\beta/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
\end{equation}
Here, we have neglected the imaginary component of $\gamma$ because it merely gives rise to a small correction to the
phase velocity  of the mode.

@@

We can combine the previous two results to give the composite layer response equation
\begin{equation}\label{e389}
{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{0}+ {\mit\Delta}\omega_E),
\end{equation}
where $\tau_s=\tau_R\,\hat{\delta}$, 
\begin{equation}
\hat{\delta} = \frac{\hat{\delta}_{\rm VR}\,\hat{\delta}_{\rm HR}}{\hat{\delta}_{\rm VR} + \hat{\delta}_{\rm HR}},
\end{equation}
and 
\begin{equation}
\omega_{0}= \omega_{\perp\,e}.
\end{equation}

@@

\subsection{Locking to Static Error-Field}\label{error}
Rotation braking due to interaction with a resistive wall can reduce the phase velocity of a tearing mode
by a large factor, but it cannot reduce the velocity to zero (because the braking torque is zero when $\omega=0$).
The later goal can be achieved by locking to a static error-field, a process that is greatly facilitated once the phase
velocity of the tearing mode has been reduced to a comparatively small value by wall braking.

>>>>

\subsection{Resonant Layer Physics}\label{sres}
By analogy with Equation~(\ref{e133}), we can write
\begin{equation}\label{e134}
{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,{\mit\Psi}_s\right).
\end{equation}
Here, $\tau_s$ is the {\em reconnection time}\/ (i.e., the typical timescale on which magnetic reconnection takes place in the
resonant layer surrounding the resonant surface), whereas $\omega_s$ is the {\em natural frequency}\/ of the tearing mode. The natural frequency is defined as oscillation frequency of a naturally unstable tearing mode. The
natural frequency  is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
flow (Fitzpatrick 1993). (See Sections~\ref{s6.2} and \ref{sphase1}.)

@@

\subsection{No-Slip Constraint}\label{sns}
The reconnected magnetic flux at the resonant surface is assumed to convected by the local plasma flow. (See Section~\ref{sres}.) Hence, changes in the
plasma flow at the resonant surface induced by the electromagnetic torques that develop in the vicinity of this
surface will modify the convection velocity. Consequently, the natural frequency of the tearing mode can be written
\begin{equation}\label{e200}
 \omega_s(t) = \omega_{s\,0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
 \omega_{s\,0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
\end{equation}
where $\omega_{s\,0}$ is the unperturbed natural frequency. The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980). 
It follows from Equations~(\ref{e190})
and (\ref{e191}) that
\begin{equation}\label{e201}
\omega_s(t) = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
\end{equation}
(See Section~\ref{stb}.)

\subsection{Final Equations}
Equations~(\ref{e123}), (\ref{e133}), (\ref{e134}),  (\ref{e145})--(\ref{e151}), (\ref{e198}), (\ref{e199}), and (\ref{e201})
can be combined to give the following complete set of equations that determine the time evolution of the reconnected 
magnetic flux at the resonant surface:
\begin{align}\label{e202}
{\mit\Delta\hat{\Psi}}_s\equiv \tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
\tau_w\,\frac{d\hat{\mit\Psi}_w}{dt} &= E_{sw}\,\hat{\mit\Psi}_s +\tilde{E}_{ww}\,\hat{\mit\Psi}_w
+\hat{I}_c,\label{e203}\\[0.5ex]
\omega_s(t)& = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\label{e210a}\\[0.5ex]
(1+2\,q_s^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1\,p}^{\,2}}{\tau_{M}}\right)\alpha_p
&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1\,p})]^{\,2}}
\,{\rm Im}({\mit\Delta\hat{\Psi}}_s\,\hat{\mit\Psi}_s^{\,\ast}),\label{e205}\\[0.5ex]
\frac{d\beta_p}{dt} + \frac{j_{0\,p}^{\,2}}{\tau_{M}}\,\beta_p
&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0\,p})]^{\,2}}\,
{\rm Im}({\mit\Delta\hat{\Psi}}_s\,\hat{\mit\Psi}_s^{\,\ast}).\label{e206}
\end{align}
Here, 
\begin{align}
\hat{I}_c &= \left(\frac{r_w}{r_c}\right)^m\frac{\mu_0\,I_c}{R_0\,B_z},\\[0.5ex]
\tilde{E}_{ww} &= E_{ww} + \frac{2m\,(r_w/r_c)^{2m}}{1-(r_w/r_c)^{2m}}.\label{e208}
\end{align}

\section{Reduced Resonant  Response Model}\label{ff}
\subsection{Introduction}
Equations~(\ref{e202})--(\ref{e206}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
natural frequency, $\omega_{s\,0}$---that can only be determined by solving for the plasma response in the radially-thin resonant layer surrounding the resonant surface. Unfortunately, determining the resonant plasma response is not a straightforward task. The
problem is that the small characteristic lengthscale in the resonant region (i.e., the resonant layer width) causes the fundamental ordering parameters
$\delta_e$ and $\delta_i$ (see Section~\ref{s3.9}) to take values that are of order unity. Consequently, most of the simplifications described in
Section~\ref{lowest} are not applicable in the resonant layer. In particular, many of the terms in the Braginskii equations (see Section~\ref{sbrag}) that are negligible in the outer region (e.g., plasma resistivity) have to be taken into account in the resonant layer.

@@

\subsection{Derivation of Linear Layer Equations}\label{s5.3}
Suppose that the system is perturbed by a tearing mode with $m$ periods in the poloidal direction, and
$n$ periods in the toroidal direction. In accordance with Equations~(\ref{e287})--(\ref{e290}), and (\ref{e292})--(\ref{e293}), we can write
\begin{align}\label{e295}
\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
U(\hat{x},\zeta,\hat{t}) &=  \hat{\nabla}^2\tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e300}
\end{align}
where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the natural frequency of the tearing mode in the laboratory frame. 
Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear layer equations:
\begin{align}\label{e301}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} \\[0.5ex]
&\phantom{=}
+S^{-1}\,P_\parallel\!\left(m\,\omega_{\ast\,e}\,\tau_H\,\hat{x}\,\tilde{\psi}-\frac{m}{\hat{L}_s}\,\hat{x}^2\,\tilde{N}\right)
+ S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\nonumber\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e304}
\end{align}
Here, 
\begin{equation}\label{e313a}
\tau_H = \frac{L_s}{m\,V_A}
\end{equation}
is the {\em hydromagnetic time}, 
\begin{equation}
\omega_E = \left(\frac{m}{r_s}\right)V_E(r_s)
\end{equation}
  the 
{\em E-cross-B frequency}, 
\begin{equation}
\omega_{\ast\,e} = -\left(\frac{\tau}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
\end{equation}
  the {\em electron diamagnetic
frequency},
\begin{align}\label{omegai}
  \omega_{\ast\,i} &= \left(\frac{1}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
  \end{align}
    the {\em ion diamagnetic
frequency}, 
\begin{equation}
S=\frac{\tau_R}{\tau_H}
\end{equation}
 the {\em Lundquist number}, 
\begin{equation}\label{e317a}
\tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel}
\end{equation}
 the
{\em resistive diffusion time}, 
\begin{equation}\label{e318a}
\tau_\varphi
= \frac{r_s^{\,2}}{\chi_\varphi}=\frac{r_s^{\,2}\,n_0\,m_i}{\mu_\perp(r_s)}
\end{equation} 
the {\em toroidal momentum confinement time}, and 
\begin{equation}
\tau_\perp = \frac{r_s^{\,2}}{D_\perp}
\end{equation}
 the {\em particle/energy confinement time}. Furthermore, $P_\varphi = \tau_R/\tau_\varphi$, $P_\perp = \tau_R/\tau_\perp$, 
$P_\parallel=\tau_R/\tau_\parallel$, and $\tau_\parallel =r_s^{\,2}/D_\parallel$.

@@

Suppose that the resonant layer lies in a constant-$\psi$ response regime. According to Equation~(\ref{e295}),
the perturbed magnetic flux in the layer takes the form:
\begin{equation}
\hat{\psi}(\hat{x},\zeta,\hat{t}) = \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},
\end{equation}
where $\tilde{\psi}$ is a complex constant. Of course, the physical flux is the real part of the previous expression; that is,
\begin{equation}\label{e352a}
\hat{\psi}(\hat{x},\xi)= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ |\tilde{\psi}|\,\cos\xi,
\end{equation}
where
\begin{equation}
\xi = \zeta +{\rm arg}(\tilde{\psi})-\hat{\omega}\,\hat{t} = m\,\theta-n\,\varphi +{\rm arg}(\tilde{\psi}) -\omega\,t.
\end{equation}
Now, it is clear from Equation~(\ref{e279}) that ${\bf B}\cdot\hat{\nabla}\hat{\psi}=0$. In other words, the contours of
$\hat{\psi}(\hat{x},\xi)$ map out the perturbed magnetic flux-surfaces in the vicinity of the resonant layer. 
Let $\hat{W} = 4\,(\hat{L}_s\,|\tilde{\psi}|)^{1/2}$. Equation~(\ref{e352a}) can be written
\begin{equation}
\frac{\hat{\psi}(\hat{x},\xi)}{|\tilde{\psi}|} = 8\left(\frac{\hat{x}}{\hat{W}}\right)^2 + \cos\xi.
\end{equation}
Figure~\ref{f2a} shows the contours of $\hat{\psi}(\hat{x},\xi)$ specified by the previous equation. It can be seen that the
tearing mode has reconnected magnetic field-lines to produce a {\em helical magnetic island chain}\/ centered on the resonant
surface ($\hat{x}=0$). The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the helical phase velocity $\omega$. The maximum full (as opposed to half) radial width of the magnetic separatrix is 
\begin{equation}\label{e355s}
W =  \hat{W}\,r_s= 4\,(\hat{L}_s\,|\tilde{\psi}|)^{1/2}\,r_s = 4\left(L_s\,R_0\,|\hat{\mit\Psi}_s|\right)^{1/2},
\end{equation}
where ${\mit\Psi}_s = r_s\,B_z\,\tilde{\psi}$ is the reconnected magnetic flux defined in Equation~(\ref{e99}), and
$\hat{\mit\Psi}_s= {\mit\Psi}_s/(R_0\,B_z)$.

@@

\subsection{Linear Dispersion Relation}\label{s6.2}
Let us write
\begin{equation}\label{e350}
\omega = {\rm i}\,\gamma+\omega_r,
\end{equation}
where $\gamma$ is the growth-rate of the tearing mode, whereas $\omega_r$ is the real
frequency of the mode in the laboratory frame. We shall assume that $|\gamma|\ll |\omega_r|$. This assumption can
easily be verified {\em a posteriori}. Asymptotic matching between the solution in the outer region and that in the
thin linear layer surrounding the resonant surface yields a linear tearing mode dispersion relation of the form
\begin{equation}\label{e352}
S^{1/3}\,\hat{\mit\Delta}(\gamma,\omega_r) = E_{ss},
\end{equation}
where use has been made of Equations~(\ref{e110}) and (\ref{e312}). Here, $E_{ss}$ is the real tearing stability index, 
whereas the complex layer matching parameter, $\hat{\mit\Delta}$, is defined in Equation~(\ref{e311}).

@@

Suppose that $Q_\ast\gg P\,p^2$ and $P\ll Q_\ast\,D^2$. It follows that $\nu=1/2$ and
\begin{equation}
C = {\rm i}\left(\frac{\tau}{1+\tau}\right)\frac{Q_\ast}{D^2}.
\end{equation} 
Hence, 
\begin{equation}
\hat{\mit\Delta} = {\rm e}^{{\rm i}\,\pi/4}\,\pi\,\hat{\gamma}\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{Q_\ast^{1/2}}{D},
\end{equation}
and $p_\ast\sim D/Q_\ast^{1/2}$. This so-called {\em semi-collisional regime}\/ is valid when $P\ll Q_\ast^{\,2}/D^2$ and
$P\ll Q_\ast\,D^2$. 
The corresponding tearing mode growth-rate is
\begin{equation}\label{e368}
\gamma = \frac{E_{ss}}{\sqrt{2}\,\pi}\,\frac{d_\beta/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
\end{equation}
Here, we have neglected the imaginary component of $\gamma$ because it merely gives rise to a small correction to the
real frequency of the mode.

@@

We can combine the previous two results to give the composite layer response equation
\begin{equation}\label{e389}
{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E),
\end{equation}
where $\tau_s=\tau_R\,\hat{\delta}$, 
\begin{equation}
\hat{\delta} = \frac{\hat{\delta}_{\rm VR}\,\hat{\delta}_{\rm HR}}{\hat{\delta}_{\rm VR} + \hat{\delta}_{\rm HR}},
\end{equation}
and 
\begin{equation}
\omega_{s\,0}= \omega_{\perp\,e}.
\end{equation} 
Here, $\omega_{\perp\,e}$ is understood to take its unperturbed (by any electromagnetic torques that
develop in the resonant layer) value.

@@

\subsection{Locking to Static Error-Field}\label{error}
Rotation braking due to interaction with a resistive wall can reduce the rotation frequency of a tearing mode
by a large factor, but it cannot reduce the frequency to zero (because the braking torque is zero when $\omega=0$).
The later goal can be achieved by locking to a static error-field, a process that is greatly facilitated once the phase
velocity of the tearing mode has been reduced to a comparatively small value by wall braking.
